\documentclass[12pt]{article}

\usepackage{fullpage}
\usepackage{/home/nick/Documents/analysis}
\usepackage{listings}
\usepackage{verbatim}

\begin{document}
\title{FrameLab\\\small{Software for framelet-based numerical analysis}}
\author{Nick Henscheid\\\small{ University of Arizona Program in Applied Mathematics}}
\date{\today}
\maketitle

\paragraph{Goals}
The idea of this project is to develop a complete software suite for computational imaging via framelets.  The code will be sorted into the following general categories: 

\begin{enumerate}
\item Framelet expansion code 
\begin{itemize}
\item Fast single and multilevel decomposition and reconstruction for 1D through 3D
\item Signal sparsity analysis, best basis selection?
\item Computing framelet coefficients 
\end{itemize}
\item Numerical optimization code 
\begin{itemize}
\item $l_1$ compressed sensing via ADMM/AL/DAL 
\item Comparison of different algorithms?
\item $l_0$ code 
\end{itemize}
\item Utilities 
\begin{itemize}
\item Graphics and figure creation 
\item Shrinkage designer 
\item PDEs for image processing
\item Forward/adjoint operators for imaging 
\item Classical signal processing 
\end{itemize}
\item Applications 
\begin{itemize}
\item CT 
\item MRI 
\item SPECT 
\item Segmentation 
\item Registration? 
\item Deblurring 
\item Deconvolution 
\item Integral equations?
\item Matrix factorization?
\item Matrix completion 
\item BM3D
\end{itemize}
\end{enumerate}


\section{Implementation Details}

\paragraph{Programming languages and interfaces}
To do: 
\begin{itemize}
\item GPU interface to python?  pycuda?  (e.g. python alternative to mex)
\end{itemize}

\paragraph{Data Types}



\section{Framelet Expansions}
The first task to create/modify functions to perform framelet decomposition and reconstruction 


\section{Optimization Methods}
%\lstinputlisting[numbers=left,language=Matlab,frame=single,caption={}Matlab function to solve the analysis-based sparse recovery problem via Augmented Lagrangian.]{../optimization/ALsolve.m}


\section{Imaging Systems}  
\subsection{2D Computed Tomography}


\subsection{3D Computed Tomography}

 
\section{Test Scripts}
\begin{enumerate}
\item testAdjoint.m
\item testBall.m
\item testCBCTCGLS.m 
\item testCBCTInterp.m
\item testCBCTInterpAugmented.m
\item testCGLSClass.m
\item testConeBeamScanner.m
\item 
\end{enumerate}



\end{document}